\chapter{Appendix A} 
\label{appendix:anexo1}

\section{Discrimination of fishing licenses}

{\Large \textbf{ Siege:}}
The purse seine used on the mainland is characterized by the use of a catch at the bottom of the net - this allows the net to be closed like a bag in order to retain the catch.

{\Large\textbf{Dragging:}}
\textbf{Drag of Doors: }A bottom-trawl net towed by a single vessel, the horizontal opening of which is ensured by relatively heavy trawl doors, which may be fitted with a steel shoe designed to withstand a contact with the bottom.
\textbf{Pole drag:} Rod trawling is characterized as a medium-sized trawl art where the mouth, devoid of wings, is held open by the action of two rods or a horizontal rod and rigid lateral structures.
Dredge: Small and medium-sized trawling art in which the mouth is composed of a rigid structure and the bag is mesh or made up of a metal grid.

{\Large\textbf{Gillnets and Trammel nets:}}
Fishing method using a rectangular net with one, two or three rafts held upright by floatation cables and cables of used ballast insulated or in hunting.

{\Large\textbf{Fishhook:}}
A fishing method that uses lines and, in general, one or more hooks, ballasts and buoys. It can be practiced with gear that is integrated in the following groups: troll, cane and hand line, longline, tone and fishing nipple.

{\Large\textbf{Traps:}}
\textbf{Cage Traps:} Fishing method by which the prey is attracted or referred to a device that prevents leakage. 
\textbf{Shelter Traps:} Fishing method by which the prey is attracted or referred to a device, in this case the pots.

{\Large\textbf{Sliding Enclosures:}}
Método de pesca que utiliza uma estrutura de rede com bolsa e grandes asas laterais que arrastam e, previamente ou em simultâneo, envolvem ou cercam.

{\Large\textbf{Catch:}}
Uses several simple utensils. It can be practiced by an individual, using or not a support vessel and apnea diving equipment.

This data is available in https://www.dgrm.mm.gov.pt 
